Changelog

### 2021-05-23 Chapter-2/Chapter-2.tex
Updates from Overleaf

\subsubsection*{Software Patching}
Once we have identified side-channel leakages, there are two common approaches to mitigate side-channel attacks in libraries. The first approach is to adopt unified behavior code when computing the secret data. For example, a control flow leakage happens when different secret inputs lead to different paths. Software can mitigate the leakage by executing both branches and select the result with the bit-wise operations.   However, for exiting code base, it is hard to migrate all the code into a constant-time implementation. The second approach is to introduce randomized behaviors during the execution to obfuscate the information that an attacker can retrieve. One example is cryptographic blinding. Side-channel attacks allow an adversary to retrieve information by measuring something other than the program's output itself. Binding values can alter the input to some unpredictable data and introduce the randomization to the execution. However, the binding value can also be retrieved by an attacker through other methods, including side-channel attacks. An attacker can launch an attack to retrieve the binding value to recover the secret input.
\subsection{Hardware Countermeasures}
\subsubsection*{Resource Partitioning}
\subsubsection*{Randomization}

>>>>

\subsubsection*{Software Patch}
Once we have identified side-channel leakages, there are two common approaches to mitigate side-channel attacks. The first approach is to adopt unified behavior code when computing the secret data. For example, a control flow leakage happens when different secret inputs lead to different paths. Software developers can mitigate the leakage by executing both branches and select the result with bit-wise operations.   However, for exiting code base, it is hard to migrate all the code into a side-channel free implementation. The second approach is to introduce randomized behaviors during the execution to obfuscate the information that an attacker can retrieve. One example is cryptographic blinding. Developers can use a random value to blend the secret key but still generate the same encrypted data with a carefully designed algorithm.  Binding values can alter the program execution to some unpredictable states and introduce the randomization to the execution. However, the binding value can also be retrieved by an attacker through other methods, including side-channel attacks. An attacker can launch an attack to retrieve the binding value to recover the secret input.
\subsection{Hardware Countermeasures}
\subsubsection*{Resource Partitioning}
\subsubsection*{Randomization}

### 2021-05-23 SupplementaryMaterial/Abstract.tex
Updates from Overleaf

%\vspace{-0.3in}
Side-channel vulnerabilities can leak secret information through non-functional characteristics, e.g., time, power, and memory usage. Like many other software vulnerabilities, attackers exploit flaws in designs of hardware and implementations of software. Hardware countermeasures, which usually require changes to the complex underlying hardware, are hard to adopt in practice. On the contrary, software approaches are generally easy to implement. This dissertation studies various aspects of side-channel vulnerabilities.

The dissertation first introduces a new method to detect address-based side-channel vulnerabilities in the binary code. While existing approaches can identify side-channel leakages in real-world programs, many these approaches are computationally expensive and need to apply domain knowledge to simplify the analysis.  We examine the bottleneck in the symbolic approaches and propose methods to identify side-channel vulnerabilities in real-world cryptography applications. We implement the approach in a tool and apply it to popular cryptography libraries. The evaluation results confirm that the tool is much faster than state-of-art tools while identifying all the known leakages reported by previous tools. In addition, our tool catches new vulnerabilities that are missed by previous tools. We confirm those vulnerabilities with manual checking and by contacting the developers.

Second, current side-channel detection tools are able to identify numerous potential vulnerabilities. However, in practice, many such vulnerabilities leak a negligible amount of sensitive information, and thus developers are often reluctant to address them. Existing tools do not provide information to evaluate a leak’s severity, such as the number of leaked bits. To address this issue, we propose a new program analysis method to precisely quantify the leaked information in a single-trace attack through side-channels. It can identify covert information flows in programs that expose confidential information and can reason about security flaws that would otherwise be difficult, if not impossible, for a developer to find. We model an attacker’s observation of each leakage site as a constraint. We use symbolic execution to generate these constraints and then run Monte Carlo sampling to estimate the number of leaked bits for each leakage site. By applying the Central Limit Theorem, we provide an error bound for these estimations. We have implemented the technique in a tool called \tool{} and apply \tool{} on OpenSSL, mbedTLS, Libgcrypt, and Monocypher. Our results demonstrate that most reported vulnerabilities are difficult to exploit in practice and should be de-prioritized by developers. The evaluation results show that our method can successfully distinguish severe leakages from many negligible leakages.

Third, we extend our approach to quantify side-channel leakages from multiple trace attacks. In this work, we present \ctool{}, an address-based side-channel detection and quantification tool that can quantify the side-channel leakages in a conservation but precise way. Unlike previous side-channel detection tools, our approach can identify those severe side-channel leakages without false positives. Moreover, by applying the chi-squared test, our tool can estimate the total effect of multiple leakage sites as well. \ctool{} consists of three steps. First, the target program is executed with a number of different sensitive inputs to record memory accesses. Second, the long address traces are split into several segments based on the location in the source code. Finally, we analyze the memory-access information from those segments and compare the address access information with the original source code. Based on the channel capacity between the original secrets and the observation of the attacker, we quantify the information leakages for each leakage site. We evaluate \ctool{} with OpenSSL, mbedTLS, TinyDNN and GTK. Our evaluation results show \ctool{} is effective in identifying and quantifying side-channel leakages.

This dissertation research develops fundamental and practical techniques for precise side-channel 
analysis in software systems. We have also open sourced our research software prototypes.
As a result, developers can use our tools to develop more secure systems and the academic and industry
communities can further advance side channel analysis on top of our research.

>>>>

\vspace{-0.3in}
Side channels are ubiquitous in modern computer systems as sensitive
information can leak through many mechanisms such as power consumption, 
execution timing, and even electromagnetic radiation. Among them, 
address-based side-channel attacks, such as cache-based attacks, 
memory page attacks, and controlled-channel attacks, are especially
problematic as they do not require physical proximity. Hardware 
countermeasures, which usually require changes to the complex 
underlying hardware, are hard to adopt in practice.  On the contrary, 
software approaches are generally easy to implement. While some existing 
tools can detect side-channel leakages, many of these approaches are 
computationally expensive or imprecise. Besides, many such vulnerabilities 
leak a negligible amount of sensitive information, and thus developers 
are often reluctant to address them. Existing tools do not provide sufficient 
information, such as the amount of information leakage through side channels, 
to evaluate the severity of a vulnerability.

In this dissertation, we present methods to detect and quantify 
address-based side-channel vulnerabilities in real-world applications. 
First, a new method to detect address-based side-channel vulnerabilities 
for the binary code is proposed. We examine the bottleneck in the symbolic 
approaches and improve the analysis precision and performance.
Second, we propose a new program analysis method to precisely quantify
the leaked information in a single-trace attack. We model an
attacker’s observation of each leakage site as a constraint and run
Monte Carlo sampling to estimate the number of leaked bits for each
leakage site. Finally, we extend our approach to quantify side-channel 
leakages from multiple trace attacks. We present a method to quantify
the lower bound of side-channel leakages. Unlike the previous side-channel 
detection tools, our approach can identify severe side-channel
leakages without false positives.

We implement the approaches and apply them to popular cryptography libraries.  
The evaluation results confirm that our side-channel detection method 
is much faster than state-of-art tools while identifying all the known leakages 
reported by previous tools.
The experiments also show that 
our side channel analysis reports quite precise leakage information
that can help developers better triage the reported vulnerabilities.
This dissertation research develops fundamental and practical techniques for precise side-channel 
analysis in software systems. We have also open sourced our research software prototypes.
As a result, developers can use our tools to develop more secure systems and the academic and industry
communities can further advance side channel analysis on top of our research.
